### 2020-11-08 README.Rmd
included new data files, ctrl, zone1, and constants with which to test the framework.

You can install the development version from [GitHub](https://github.com/haddonm/aMSE) with:

@@

Alternatively, you can generate a branch that you can work on by cloning the repository, which, again, can be done very simply within RStudio. Open the New Project option in the project dialog at the top right of the RStudio screen and selection Version Control, then use 'https://github.com/haddonm/aMSE' in the top box, identify where you want the new directory put, and press return.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the resdir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
resdir <- paste0(ddir,"aMSEUse/conddata/generic2")  # data and results directory
dirExists(resdir,make=TRUE,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, zone1.csv
# and region1.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate(),
# and zonefiletemplate.
zone1 <- readctrlzone(resdir,infile="control.csv")
ctrl <- zone1$ctrl
glb <- zone1$globals     # glb without the movement matrix
constants <- readdatafile(glb$numpop,resdir,ctrl$datafile)
#zone1$initLML <- 140
out <- setupzone(constants,zone1) # make operating model
zoneC <- out$zoneC
zoneD <- out$zoneD
glb <- out$glb             # glb now has the movement matrix
product <- out$product     # important bits usually saved in resdir
# did the larval dispersal level disturb the equilibrium?
zoneD <- testequil(zoneC,zoneD,glb)
zoneC <- resetexB0(zoneC,zoneD) # rescale exploitB to avexplB after dynamics
initialC <- zoneC
unfishedD <- zoneD         # keep a copy of the unfished zone

>>>>

Once the MSE framework is made public you can install the development version from [GitHub](https://github.com/haddonm/aMSE) with:

@@

Alternatively, while the development version remains private, you can generate a branch that you can work on by cloning the repository, which, again, can be done very simply within RStudio. Open the New Project option in the project dialog at the top right of the RStudio screen and selection Version Control, then use 'https://github.com/haddonm/aMSE' in the top box, identify where you want the new directory put, and press return. ALternatively, you could download the zip file from inside the 'code' button and establish an R project from that.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the resdir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
resdir <- paste0(ddir,"aMSEUse/conddata/generic2")  # data and results directory
dirExists(resdir,make=TRUE,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, zone1.csv
# and region1.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate(),
# and zonefiletemplate.  In the meantime it is easier to use the included 
# data files. The original csv files are included in the data-raw directory
data(ctrl)
data(zone1)
data(constants)
ctrl$reps <- 250  # the original = 1000, we use 250 to use only 25% of the time
#zone1$initLML <- 140
out <- setupzone(constants,zone1) # make operating model
zoneC <- out$zoneC
zoneD <- out$zoneD
glb <- out$glb             # glb now has the movement matrix
product <- out$product     # important bits usually saved in resdir
# did the larval dispersal level disturb the equilibrium?
zoneD <- testequil(zoneC,zoneD,glb)
zoneC <- resetexB0(zoneC,zoneD) # rescale exploitB to avexplB after dynamics
initialC <- zoneC
unfishedD <- zoneD         # keep a copy of the unfished zone
